Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-24 paper/ijcai/paper.tex
redo

As to quantify complexity of fault localization on this dataset, we
additionally counted the number of cases of ``fault of omission'', a
popular metric in fault localization research for that
purpose~\Fix{cite}\Sof{Not sure what to cite here}. A fault of omission occurs when
the program is buggy because some code is missing, i.e., a bug that is 
corrected by adding code. Intuitivelly, 
the ability of techniques to
produce good diagnosis in those cases reduce as \Fix{...explain...}. A
total of $59.7\%$ of the cases in this dataset manifest fault of
omission, which is a good indication of difficulty.

@@

A necessary but insufficient condition for improvement of fault
localization with \comb{} is that dynamic slicing eliminates a high
amount of code in the best ranked files. Table \ref{tab:red} shows, as
percentages, the average reduction on the sum of top file sizes
obtained with dynamic slicing for different values of
$k$.\Mar{$\leftarrow$sofia, please check.} Overall, results indicate
that dynamic slicing substantially reduces the size of highly-ranked
files. \Mar{sofia, it would be more convincing if you (additionally)
  show reduction wrt to the the parts of the file that are covered.}

@@

\begin{table*}[t!]
	\small
	% \setlength{\tabcolsep}{3pt}
	\centering
	  \begin{tabular}{l|cc|cc|c}
		\toprule
		 Project        &   \sfl{}$^{5}$   & \combpar{5}
		 				&   \sfl{}$^{10}$   & \combpar{10}& \# Faults      \\
		\midrule
		 \lang{}         &   84.6   & 100.0 & 84.6 & 96.9  \\
		\cmath{}           & 81.7 & 89.4 & 85.6 & 95.2 \\
		\chart{}           & {\cellcolor{Gray} 84.6} & {\cellcolor{Gray}76.9} & {\cellcolor{Gray}92.3} & {\cellcolor{Gray}84.6}\\
		\jtime{}           & 77.8 & 81.5 & 81.5 & 85.2\\
		\mockito{}           & 63.2 & 71.1 & 71.1 & 78.9\\   \midrule
		Total         & 79.6 & 87.3 & 83.5 & 91.2\\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the faulty-statements is in the \sfl{}$^{k}$ and \combpar{k} report}
  \label{table:fsws}
\end{table*}

>>>>

As to quantify complexity of fault localization on this dataset, we
additionally counted the number of cases of ``fault of omission'', a
popular metric in fault localization research for that
purpose~\Fix{cite}\Sof{Not sure what to cite here}. A fault of omission occurs when
the program is buggy because some code is missing, i.e., a bug that is 
corrected by adding code. Intuitivelly, the ability of techniques to
produce good diagnosis in those cases is poor since fault of omission
are non-executable statements which means that the execution information
cannot help locate the fault directly. A total of $59.7\%$ of the cases 
in this dataset manifest fault of omission, which is a good indication of 
difficulty\Sof{note to self: Improve the good indication of difficulty}.

@@

A necessary but insufficient condition for improvement of fault
localization with \comb{} is that dynamic slicing eliminates a high
amount of code in the best ranked files. Table \ref{tab:red} shows, as
percentages, the reduction of the top file sizes
obtained with dynamic slicing for different values of
$k$. Overall, results indicate
that dynamic slicing substantially reduces the size of highly-ranked
files. \Mar{sofia, it would be more convincing if you (additionally)
  show reduction wrt to the the parts of the file that are covered.}

@@

\begin{table}[h!]
	\small
	\setlength{\tabcolsep}{3pt}
	\centering
\begin{tabular}{l|rr|rr}
		 \toprule
       & \multicolumn{2}{c|}{$k=5$} & \multicolumn{2}{c}{$k=10$} \\
		 Project        &   \sfl{}   & \comb &   \sfl{}   & \comb\\
		\midrule
		 \lang{}         &   84.6   & 100.0 & 84.6 & 96.9  \\
		\cmath{}           & 81.7 & 89.4 & 85.6 & 95.2 \\
		\chart{}           & {\cellcolor{Gray} 84.6} & {\cellcolor{Gray}76.9} & {\cellcolor{Gray}92.3} & {\cellcolor{Gray}84.6}\\
		\jtime{}           & 77.8 & 81.5 & 81.5 & 85.2\\
		\mockito{}           & 63.2 & 71.1 & 71.1 & 78.9\\   \midrule
		Total         & 79.6 & 87.3 & 83.5 & 91.2\\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the faulty-statements is in the \sfl{}$^{k}$ and \combpar{k} report}
  \label{table:fsws}
\end{table}
